---
title: "Sampling of papers for survey (2024)"
author: "Bartosz Maćkiewicz"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(bib2df) # for importing bibtex file
library(tidyverse) # for general data manipulation
```

# Preparation of the data

1. We load data from PhilPapers "experimental philosophy" category (curated by James Andow) downloaded at 2025-01-13 03:32 GMT+1. This file was downloaded in the BibTeX format and reformatted with `biber.

```{r}
data <- bib2df("experimental_philosophy_philpapers_13_01_2025_bibertool.bib")
data$AUTHOR <- stringi::stri_c_list(data$AUTHOR, sep=", ")
```

2. Next, we filter out all papers that are not released yet (forthcoming, manuscript, unknow) and papers which has not valid year of publication.

```{r}
data <- data %>% 
  filter(!DATE %in% c("forthcoming", "manuscript", "unknown")) %>% 
  mutate(year = as.numeric(DATE)) %>% # converting from character to numeric
  filter(year >= 2007 & year <= 2024) # before manifesto we do not expect proper x-phi
```

3. Plot of all papers in our sampling frame

```{r}
ggplot(data = data) + 
  geom_bar(aes(x=year), stat = "count")
```

```{r}
pander::pander(table(data$DATE))
```

4. Cut data into 5 bins according to date of publication:
- bin 1: [2007-2009]
- bin 2: [2010-2012] 
- bin 3: [2013-2015]
- bin 4: [2016-2018]
- bin 5: [2019-2021] (will be sampled in the future)
- bin 6: [2012-2023] (will be sampled in the future)

```{r}
# A function to help with binning 
bin_helper <- function(x, min, max, num){
  y_range <- max-min+1
  if (y_range %% num != 0){
    error("Year range not divisible by number of bins")
  }
  bin_width <- y_range / num
  for (b in 0:(num-1)){
    if ((x >= min + b * bin_width) & (x < min + (b+1) * bin_width)){
      return(b+1)
    }
  }
  return(NA)
}

data$bin <- sapply(data$year, bin_helper, 2007, 2024, 6)
```

5. Plot number of papers in each bin.

```{r}
ggplot(data = data) + 
  geom_bar(aes(x=bin), stat = "count")
```

```{r}
pander::pander(table(data$bin))
```

5. Permute papers within each bin. Save the results to XLSX file and CSV file. 
First $n=50$ from each bin that meet our criteria are included in the study.

```{r}
data <- data[!is.na(data$bin), ]
groups <- split(data, data$bin)
set.seed(54321)
for (bin in names(groups)[1:4]){ # bins 5 and 6 will be drawn later
  permuted <- sample_frac(groups[[bin]], 1)
  cat(paste0("Bin number: ", bin, "\n"))
  cat(paste0("Min YEAR: ", min(permuted$DATE), "\n"))
  cat(paste0("Max YEAR: ", max(permuted$DATE), "\n"))
  cat(paste0("Total numbers of papers in the bin: ", nrow(permuted), "\n"))
  cat("\n")
  formatted <- as.data.frame(permuted) %>% select(
    BIBTEXKEY, 
    DATE, 
    TITLE, 
    AUTHOR, 
    JOURNALTITLE,
    BOOKTITLE,
    CATEGORY, 
    DOI,
    EDITOR,
    PUBLISHER
  )
  writexl::write_xlsx(formatted, paste("data/", bin, ".xlsx", sep = ""))
  readr::write_csv(formatted, paste("data/", bin, ".csv", sep = ""))
}
```